From Nested Virtualization Architecture \\To 2D Security Management for Distributed Clouds

### 2014-03-24 paper/draft.tex
Tentative refonte Introduction
- Quelques corrections
- Deplacement plan papier

\noindent Distributed cloud computing is now becoming a reality. Modern cloud platforms are able to provide elastic use of resources, optimizing their allocation to meet user needs. However, currently deployed distributed cloud infrastructures present several limitations.

This paper is organized as follows. In Section~\ref{sec:rw} we analyze the nested virtualization ecosystem and position existing solutions regarding our design principles. In Section~\ref{sec:classic}, we details limitations of classical nested virtualization approach and in Section~\ref{sec:mh} we present the microvisor approach. In Section~\ref{sec:archcomp} we compare cloud architectures propositions, combining nested virtualization and microvisors, leveraging the design principles grid introduced before.
%Furthermore, in Section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles.
In Section~\ref{sec:conclu}, we conclude the paper with future works and our vision of the SuperCloud.
% in section in section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles. In section 8, we conclude the paper with future works in section 8.

\section{Challenges and Design Principles}

>>>>

%% Motivation
%Cloud computing platform are a solid reality nowadays. 
\noindent Distributed cloud computing is now becoming a reality. Modern cloud platforms are able to provide elastic use of resources, optimizing their allocation to meet user needs. However, currently deployed distributed cloud infrastructures present several limitations.

% Interop
DCC does not handle heterogeneous infrastructures which secludes providers in non-evolving hardware.
% Securite
Also, security remains the last hurdle toward wide adoption of DCC. The user data are no more self contained but distributed among all parties without any proof of confidentiality, integrity or availability.

%% Specific problem considered
We classified problems related to DCC horizontally and vertically. The horizontal view gathers features related to interactions between IaaS stacks, such as live migrations. The vertical view addresses features close to the isolation of execution environment on the same physical machine. This classification provide a global coverage of problems to solve to deliver a secure, stable and robust architecture.

%% "In this paper we show that"
As a first element of answer, the nested virtualization~\cite{turtle:ibm} performed a breakthrough with enhanced isolation capabilities on the same physical machine. The hypervisor is now virtualized by a thin layer~\cite{cloudvisor:zhang} to counter failures. Furthermore, the horizontal challenges were also included in this tiny layer to deliver an homogeneous interface for commodity hypervisors~\cite{art:blan, xclo:blank}. However these classic approaches suffers from several shortcomings detailed in Section~\ref{ref:challenges}. Thus we propose a novel architectural approach to undertake remaining problems.

%% Differences with others
The previous works created both horizontal and vertical basic blocks from scratch. While being a necessary step, these approaches does not inherits the advances performed in terms of operating system security. The software architecture are mainly monolithic and yet-another-layer fends off security problems without
figuring them out. Our approach learns from security issues fixed by OS architecure~\cite{} and apply these patterns to leverage nested virtualization. In this paper we show that component-based architecures are a promising design for the next generation of clouds.

This paper is organized as follows. Section~\ref{ref:challenges} details the constraints of nested virtualization for the two dimension of our solution. In Section~\ref{sec:rw} we analyze the nested virtualization ecosystem and position existing solutions regarding our design principles. In Section~\ref{sec:classic}, we details limitations of classical nested virtualization approach and in Section~\ref{sec:mh} we present the microvisor approach. In Section~\ref{sec:archcomp} we compare cloud architectures propositions, combining nested virtualization and microvisors, leveraging the design principles grid introduced before.
%Furthermore, in Section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles.
In Section~\ref{sec:conclu}, we conclude the paper with future works and our vision of the SuperCloud.
% in section in section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles. In section 8, we conclude the paper with future works in section 8.

\section{Challenges and Design Principles}
\label{ref:challenges}
